---
title: "Graphical relationship Indonesian birds"
author: "Kushal K Dey"
date: "3/25/2018"
output: html_document
---

## Intro

Here, we explore a graphical model connecting the different bird species in the Java,
Bali, Lombok, Sumbawa areas in Indonesia. We here are interested in seeing how the 
clustering of bird species into communities by the GoM model matches with 
an independently generated graphical structure of the bird species. 

## Packages

```{r message=FALSE, warning=FALSE, include = TRUE}
library(igraph)
library(RColorBrewer)
library(ape)
```

## Data 

```{r}
datalist <- get(load("../data/wallace_region_pres_ab_breeding_no_seabirds.rda"))
latlong <- datalist$loc
data <- datalist$dat

idx1 <- which(latlong[,2] > -9.3 & latlong[,2] < -7.3)
idx2 <- which(latlong[,1] > 112 & latlong[,1] < 119.5)
idx <- intersect(idx1, idx2)
length(idx)
latlong2 <- latlong[idx,]

birds_pa_data_2 <- data[idx, ]
birds_pa_data_3 <- birds_pa_data_2[, which(colSums(birds_pa_data_2)!=0)]
```

```{r}
co_occur_mat <- t(as.matrix(birds_pa_data_3)) %*% as.matrix(birds_pa_data_3)
```

## Minimal Spanning Tree (correlation)

```{r}
cor_dist <- 1 - cov2cor(co_occur_mat)
system.time(mst2 <- ape::mst(cor_dist));
mst2.graph <- igraph::graph.adjacency(as.matrix(mst2));

cols1 <- c(RColorBrewer::brewer.pal(12, "Paired")[c(3,4,7,8,11,12,5,6,9,10)],
           RColorBrewer::brewer.pal(12, "Set3")[c(1,2,5,8,9)],
           RColorBrewer::brewer.pal(9, "Set1")[c(9,7)],
           RColorBrewer::brewer.pal(8, "Dark2")[c(3,4,8)])

plot(mst2.graph,
     edge.arrow.mode=0,
     vertex.size = 5,
     vertex.shape="square",
     vertex.label=NA,
     layout= layout_with_fr
)
```

## Coloring by GoM clusters

```{r}
topics_clust <- get(load("../output/methClust_java_bali_lombok.rda"))
```

```{r}

cols1 <- c(RColorBrewer::brewer.pal(12, "Paired")[c(3,4,7,8,11,12,5,6,9,10)],
           RColorBrewer::brewer.pal(12, "Set3")[c(1,2,5,8,9)],
           RColorBrewer::brewer.pal(9, "Set1")[c(9,7)],
           RColorBrewer::brewer.pal(8, "Dark2")[c(3,4,8)])
```

### K = 2

```{r}
freq <- topics_clust[[2]]$freq
max_clus <- apply(freq, 1, function(x) which.max(x))

plot(mst2.graph,
     edge.arrow.mode=0,
     vertex.size = 5,
     vertex.shape="square",
     vertex.label=NA,
     vertex.color=cols1[as.numeric(max_clus) + 1],
     layout= layout_with_kk
)

```


### K = 3

```{r}
freq <- topics_clust[[3]]$freq
max_clus <- apply(freq, 1, function(x) which.max(x))

plot(mst2.graph,
     edge.arrow.mode=0,
     vertex.size = 5,
     vertex.shape="square",
     vertex.label=NA,
     vertex.color=cols1[as.numeric(max_clus) + 1],
     layout= layout_with_kk
)

```

### K = 4

```{r}
freq <- topics_clust[[4]]$freq
max_clus <- apply(freq, 1, function(x) which.max(x))

plot(mst2.graph,
     edge.arrow.mode=0,
     vertex.size = 5,
     vertex.shape="square",
     vertex.label=NA,
     vertex.color=cols1[as.numeric(max_clus) + 1],
     layout= layout_with_kk
)

```


## SessionInfo

```{r}
sessionInfo()
```



